\documentclass[12pt, letterpaper]{article}
\usepackage{amsmath}
\usepackage[a4paper, total={6in, 10in}]{geometry}
\usepackage[ruled]{algorithm2e}
\usepackage{caption}
\usepackage[utf8]{inputenc}

\begin{document}

\section{Exercise 6.4}

\subsection{Problem}

You are given a string of \(n\) characters \(s[1 \dots n]\),which you believe to be a corrupted text document in which all punctuation has vanished (so that it looks something like “itwasthebestoftimes...”). You wish to reconstruct the document using a dictionary, which is available in the form of a Boolean function \(dict(\cdot)\): for any string \(w\),
\begin{center}
    \(
        dict(w) = 
        \begin{cases}
            true,& \text{if } w \text{ is a valid word} \\
            false,& \text{otherwise}
        \end{cases}
    \)
\end{center}

\begin{itemize}
    \item[(a)] Give a dynamic programming algorithm that determines whether the string \(s[\cdot]\) can be reconstituted as a sequence of valid words. The running time should be at most \(O(n^2)\), assuming calls to \(dict\) take unit time.
    \item[(b)] In the event that the string is valid, make your algorithm output the corresponding sequence of words.
\end{itemize}

\subsection{Example Case}

Below are the tabular results of \(dict(s_j,\dots,s_i)\) where \(i\) is rows and \(j\) is columns for the given string "\emph{itwasthebest}".

\begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
    \hline
    & & \(1\) & \(2\) & \(3\) & \(4\) & \(5\) & \(6\) & \(7\) & \(8\) & \(9\) & \(10\) & \(11\) & \(12\) \\
    \hline
    & \((i/j)\) & \(i\) & \(t\) & \(w\) & \(a\) & \(s\) & \(t\) & \(h\) & \(e\) & \(b\) & \(e\) & \(s\) & \(t\) \\
    \hline
    1 & \(i\) & 1 & - & - & - & - & - & - & - & - & - & - & - \\
    2 & \(t\) & 1 & 0 & - & - & - & - & - & - & - & - & - & - \\
    3 & \(w\) & 0 & 0 & 0 & - & - & - & - & - & - & - & - & - \\
    4 & \(a\) & 0 & 0 & 0 & 1 & - & - & - & - & - & - & - & - \\
    5 & \(s\) & 0 & 0 & 1 & 1 & 0 & - & - & - & - & - & - & - \\
    6 & \(t\) & 0 & 0 & 0 & 0 & 0 & 0 & - & - & - & - & - & - \\
    7 & \(h\) & 0 & 0 & 0 & 0 & 0 & 0 & 0 & - & - & - & - & - \\
    8 & \(e\) & 0 & 0 & 0 & 0 & 0 & 1 & 1 & 0 & - & - & - & - \\
    9 & \(b\) & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & - & - & - \\
    10 & \(e\) & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & - & - \\
    11 & \(s\) & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & - \\
    12 & \(t\) & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 \\
    \hline
\end{tabular}
\end{center}

\begin{itemize}
\item Starting with \(i = 12\), \(W(12) = 1\) because \(dict(s_{j=9},\dots,s_{i=12}) = 1\) and ... 
\item \(W(j-1) = W(8) = 1\) because \(dict(s_{j=6},\dots,s_{i=8}) = 1\) and ...
\item \(W(j-1) = W(5) = 1\) because \(dict(s_{j=3},\dots,s_{i=5}) = 1\) and ...
\item \(W(j-1) = W(2) = 1\) because \(dict(s_{j=1},\dots,s_{i=2}) = 1\) and ...
\item \(W(j-1)=W(0)=1\).
\end{itemize}

\pagebreak
\subsection{Solution}

\begin{algorithm}
    \SetKwInput{KwSubproblem}{Subproblem}
    \SetKwInput{KwRecurrence}{Recurrence}
    \SetKwInput{KwTime}{Time}
    \caption{WRD1 (\(\mathcal{S}\)), returns \(s_1,\dots,s_n\) as a sequence of valid words or an empty array if the string is not a sequence of valid words.}
    \KwIn{A string \(\mathcal{S}\) consisting of characters \(s_1, \dots, s_n\).}
    \KwOut{A set of valid words \(w\) extracted from string \(\mathcal{S}\) or an empty array if not a sequence of valid words.}
    \KwSubproblem{Let \(W(i)\) indicate if the given sequence of characters \(\{s_1,\dots,s_i\}\) is a valid set of words. Let \(W(0)=1\).}
    \KwRecurrence{\(W(i) = \bigvee\limits_{j=1}^{i} dict(s_j,\dots,s_i) \land W(j-1)\)} 
    \KwTime{\(O(n^2)\) for the nested for loops.} 
    \For{\(i = 1 \to n\)} 
    {
        \For{\(j = 1 \to i\)} 
        {
            \(W(i) = dict(s_j,\dots,s_i) \land W(j-1)\) \\
            \(L(i) = min(L(i), j)\)
        }
    }
    \eIf{\(W(n) = true\)}
    {
        \ForEach{\(i \in L\)}
        {
            \(append(R, \{s_{L(i)},\dots,s_i\})\)
        }
        \Return \(R\)
    }
    {
        \Return \(false\)
    }
\end{algorithm}

\end{document}