\documentclass[12pt, letterpaper]{article}
\usepackage{amsmath} % For \cases
\usepackage[ruled]{algorithm2e}
\usepackage{caption}
\usepackage[a4paper, total={6in, 9in}]{geometry}
\usepackage[utf8]{inputenc}

\title{First document}
\author{Hubert Farnsworth \thanks{Examples referenced from https://www.overleaf.com/learn/latex/Learn\_LaTeX\_in\_30\_minutes}}
\date{February 2017}

\begin{document}

\maketitle

% This line here is a comment. It will not be printed in the document.

We have now added a title, author and date to our first \LaTeX{} document!

\section{Basic Formatting}

\subsection{Text}

Some of the \textbf{greatest}
discoveries in \underline{science} 
were made by \textbf{\textit{accident}}.
Some of the greatest \emph{discoveries} 
in science 
were made by accident.

\textit{Some of the greatest \emph{discoveries} 
in science 
were made by accident.}

\textbf{Some of the greatest \emph{discoveries} 
in science 
were made by accident.}

\subsection{Lists}

\begin{itemize}
  \item The individual entries are indicated with a black dot, a so-called bullet.
  \item The text in the entries may be of any length.
\end{itemize}

\section{Math Formatting}

\subsection{Basic}

In physics, the mass-energy equivalence is stated 
by the equation $E=mc^2$, discovered in 1905 by Albert Einstein.

\subsection{Equations}

The mass-energy equivalence is described by the famous equation
\[ E=mc^2 \]
discovered in 1905 by Albert Einstein. 
In natural units ($c = 1$), the formula expresses the identity
\begin{equation}
E=m
\end{equation}

Subscripts in math mode are written as $a_b$ and superscripts are written as $a^b$. These can be combined and nested to write expressions such as

\[ T^{i_1 i_2 \dots i_p}_{j_1 j_2 \dots j_q} = T(x^{i_1},\dots,x^{i_p},e_{j_1},\dots,e_{j_q}) \]
 
We write integrals using $\int$ and fractions using $\frac{a}{b}$. Limits are placed on integrals using superscripts and subscripts:

\[ \int_0^1 \frac{dx}{e^x} =  \frac{e-1}{e} \]

Lower case Greek letters are written as $\omega$ $\delta$ etc. while upper case Greek letters are written as $\Omega$ $\Delta$.

Mathematical operators are prefixed with a backslash as $\sin(\beta)$, $\cos(\alpha)$, $\log(x)$ etc.

\section{Tables}

\subsection{Basic}

\begin{center}
  \begin{tabular}{ c c c }
    cell1 & cell2 & cell3 \\
    cell4 & cell5 & cell6 \\
    cell7 & cell8 & cell9
  \end{tabular}
\end{center}

\subsection{Borders}

\begin{center}
  \begin{tabular}{||c c c c||}
    \hline
    Col1 & Col2 & Col2  & Col3 \\ [0.5ex]
    \hline\hline
    1    & 6    & 87837 & 787  \\
    \hline
    2    & 7    & 78    & 5415 \\
    \hline
    3    & 545  & 778   & 7507 \\
    \hline
    4    & 545  & 18744 & 7560 \\
    \hline
    5    & 88   & 788   & 6344 \\ [1ex]
    \hline
  \end{tabular}
\end{center}

\subsection{Advanced with Caption}

Table \ref{table:data} is an example of referenced \LaTeX{} elements.

\begin{table}[h!]
  \centering
  \begin{tabular}{||c c c c||}
    \hline
    Col1 & Col2 & Col2  & Col3 \\ [0.5ex]
    \hline\hline
    1    & 6    & 87837 & 787  \\
    2    & 7    & 78    & 5415 \\
    3    & 545  & 778   & 7507 \\
    4    & 545  & 18744 & 7560 \\
    5    & 88   & 788   & 6344 \\ [1ex]
    \hline
  \end{tabular}
  \caption{Table to test captions and labels}
  \label{table:data}
\end{table}

\section{Algorithms}

\begin{algorithm}
  \captionsetup{labelsep=newline}
  \caption{Tweedledee and Tweedledum}
  \SetKwInOut{Definition}{Definition}
  \Definition{Conditionally, \(
    \begin{cases}
        \{\mathcal{S}[i-1], a_i\},&\text{if }\sum_{j=1}^{i}a_j > 0\\
        \{a_i\},&\text{otherwise }
    \end{cases}
  \)}
  \KwIn{A list of numbers, \({a_1}, {a_2},\dots,{a_n}\).}
  \KwOut{The contiguous subsequence of maximum sum (a subsequence of length zero has sum zero).}
  $i\gets 10$\;
  \eIf{$i\geq 5$}
  {
    $i\gets i-1$\;
  }{
    \If{$i\leq 3$}
    {
      $i\gets i+2$\;
    }
  }
\end{algorithm}

\end{document}